Microlensing as a possible probe of event-horizon structure in quasars

### 2016-10-03 paper1/ms.tex
changes

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/M87_shape.eps}
        \includegraphics[width = 0.48\textwidth]{figures/M87_lc.eps}
\caption{\label{fig:M87_plots} The one dimensional profile obtained
  from the numerical integration along the ordonata axis of a simulated source
  image is presented in the upper panel. The source image was presented in 
 \cite{2012MNRAS.421.1517D} in the top right-most panel of figure 5 
(of the respective paper) as a result of the simulations 
presented in \cite{2009MNRAS.394L.126M}. The corresponding
  lightcurve associated to the 1D profile is presented in the lower
  panel. The points $\rm p_2$ and $\rm p_3$ mark the start and 
  end of the equivalent
  dark disk and are associated with the moments of their overlap with
  the caustic: $\rm t_2$ and $\rm t_3$. $\rm h_{w}$ denotes the maximum width of the crescent.}
\end{figure}

>>>>

\begin{figure}
\centering
    \includegraphics[width = 0.48\textwidth]{figures/M87_shape.eps}
        \includegraphics[width = 0.48\textwidth]{figures/M87_lc.eps}
\caption{\label{fig:M87_plots} The one dimensional profile obtained
  from the numerical integration along the ordonata axis of a simulated source
  image is presented in the upper panel. The source image was presented in 
 Dexter et al 2012 in the top right-most panel of figure 5 
(of the respective paper) as a result of the simulations 
presented in McKinney \& Blandford 2009. The corresponding
  lightcurve associated to the 1D profile is presented in the lower
  panel. The points $\rm p_2$ and $\rm p_3$ mark the start and 
  end of the equivalent
  dark disk and are associated with the moments of their overlap with
  the caustic: $\rm t_2$ and $\rm t_3$. $\rm h_{w}$ denotes the maximum width of the crescent.}
\end{figure}
